Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-22 edubots_surveys.Rnw
Rewriting and highlighting @noorhanabbas sentence

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed\textcolor{blue}{; this will be explained more fully in the corresponding section}.  The responses' analysis
entailed the creation of a second survey to which 200 teachers' responses were
collected\textcolor{blue}{, with the methodology and collective characteristics that will be explained below}. The questions of the second survey focussed on discussing teachers'
needs, opinions and preferences of the development of future technology-enhanced
tools and its potential impact on educational institutions’ policies. Therefore,
this paper investigated the following research questions:

>>>>

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed\textcolor{blue}{; this will be explained more fully in the corresponding section}. The responses' analysis
entailed the creation of a second survey to which 200 teachers' responses were
collected\textcolor{blue}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focussed on discussing teachers'
needs, opinions and preferences of the development of future technology-enhanced
tools and its potential impact on educational institutions’ policies. In order to assess these, this paper investigated the following research questions}:
